### 2013-11-12 src2/thesis.tex
update

Paper F (section~\ref{sec:paperF}) tells a story about how to implement and tune 
a reduction kernel in Obsidian. Seven reduction kernels are implemented, the first 
very simple and naive. Each following kernel tweaks some aspect of the previous one. 
Applying these changes is pleasingly simple using Obsidian; some of these changes 
would mean a major rewrite in CUDA. The final kernel is almost 5 times as fast as the first, 
and reaches a throughput of 140GB/sec on a GPU with 192GB/sec memory bandwidth. The speed of any 
kernel will always be limited by how fast the data can be pushed through the GPU; this performance 
is quite satisfactory. In Paper F, a large reduction algorithm based on this kernel is 
implemented that runs slightly faster than Accelerates fold skeleton. With this reduction 
case study, we have pushed Obsidian as far as possible with the current abstractions. 
However, it is possible that with more work on the warp level abstractions, this could be 
improved further.   
%faster than the reduction skeleton used in Accelerate. This is quite a feat, since 
%reduction in Accelerate corresponds to just one single hand optimised skeleton. We would have 
%been happy just getting close.

@@

An in depth comparison of Obsidian and Accelerate is hard to perform. The reason for 
this is that Obsidian is a language for kernels, while Accelerate is a language for 
applications. Any larger GPU application consists of a number of kernels that 
are cooperating. Obsidian only has very basic support for launching and coordinating 
kernels for such applications, from within Haskell and Accelerate is limited in specifying 
new specialised kernels.

>>>>

Paper F (section~\ref{sec:paperF}) tells a story about how to implement and tune 
a reduction kernel in Obsidian. Seven reduction kernels are implemented, the first 
very simple and naive. Each following kernel tweaks some aspect of the previous one. 
Applying these changes is pleasingly simple using Obsidian; some of these changes 
would mean a major rewrite in CUDA. The final kernel is almost 5 times as fast as the first, 
and reaches a throughput of 140GB/s on a GPU with 192GB/s memory bandwidth. The speed of any 
kernel will always be limited by how fast the data can be pushed through the GPU; this performance 
is quite satisfactory. In Paper F, a large reduction algorithm based on this kernel is 
implemented that runs slightly faster than Accelerates fold skeleton. With this reduction 
case study, we have pushed Obsidian as far as possible with the current abstractions. 
However, it is possible that with more work on the warp level abstractions, this could be 
improved further. Our reduction case study was based on lecture slides from 
NVIDIA~\citet{reducion}. Reference~\citet{merrill}, has much information about 
how to think about performance when programming GPUs. 
%faster than the reduction skeleton used in Accelerate. This is quite a feat, since 
%reduction in Accelerate corresponds to just one single hand optimised skeleton. We would have 
%been happy just getting close.

@@

An in depth comparison of Obsidian and Accelerate is hard to perform. The reason for 
this is that Obsidian is a language for kernels, while Accelerate is a language for 
applications. Any larger GPU application consists of a number of kernels that 
are cooperating. Obsidian only has very basic support for launching and coordinating 
kernels for such applications from within Haskell, and Accelerate is limited in specifying 
new specialised kernels.
